### 2025-05-07 sec/introduction.tex

\begin{table}[!ht]
   \centering
   \tiny
   \begin{tabular}{p{2cm}p{1.3cm}p{6.7cm}p{2cm}}
      \toprule
      Type & Category & Example & Status \\
      \midrule
      pure numerical values & Quantitative expressions & (findWithKey' "model" "LSTM" tableData).time\_s & Done \\
      percentages & Quantitative expressions &  "The Energy Sector accounts for total methane emissions of", (record.emissions / sum(map (fun x -> x.emissions) (getByYear year tableData))) * 100 & Done \\
      rounded or normalised numbers & Quantitative expressions & ~ & ~ \\
      average & Aggregation & "The average methane emissions for the year 2024 is", (sumEmissions year tableData / length records) & Done \\
      totals & Aggregation & "The total methane emissions for the year 2024 is", (sumEmissions year tableData) & Done \\
      count & Aggregation & ~ & ~ \\
      comparisons & Trends & trendWord (findWithKey' "model" "BiLSTM" tableData).time\_s (findWithKey' "model" "LSTM" tableData).time\_s "growing from" "shrinking to" "equal to" & Done \\
      ranks & Trends & let pos = findIndex "model" "CNN" (insertionSort cmpTime tableData) in rankLabel "lowest" pos & Done \\
      Graded adjectives  & Adjectives & ~ & ~ \\
      References to visual elements and their parts (mereology) & ~ & ~ & ~ \\
      \bottomrule
   \end{tabular}
\end{table}

>>>>

\begin{table}[!ht]
   \centering
   \tiny
   \renewcommand{\arraystretch}{1.5}
   \begin{tabular}{p{1.5cm}p{1.5cm}p{5cm}p{4cm}}
      \toprule
      \textbf{Category} & \textbf{Type} & \textbf{Example} & \textbf{Result} \\
      \midrule
      \rowcolor{green!20}
      Quantitative expressions & Pure numerical values &
      \begin{lstlisting}[language=Fluid]
            (findWithKey' "model" "LSTM" tableData).time\_s
      \end{lstlisting}
      & 67 \\
      \rowcolor{green!20}
      Quantitative expressions & Percentages &
      \begin{lstlisting}[language=Fluid]
         "The Energy Sector accounts for total methane emissions of", (record.emissions / sum(map (fun x -> x.emissions) (getByYear year tableData))) * 100, "in 2030"
      \end{lstlisting} &
      The Energy Sector accounts for total methane emissions of 52.80\% in 2030.\\
      \rowcolor{green!20}
      Quantitative expressions & Rounded or normalised numbers & ~ & ~ \\
      \rowcolor{green!20}
      Aggregation & Average &
      \begin{lstlisting}[language=Fluid]
         The average methane emissions for the year 2030 is, (sumEmissions year tableData / length records)
      \end{lstlisting}
      & The average methane emissions for the year 2030 is 13.51 \\
      \rowcolor{green!20}
      Aggregation & Totals &
      \begin{lstlisting}[language=Fluid]
         "The total methane emissions for the year 2030 is", (sumEmissions year tableData), "for Agriculture"
      \end{lstlisting} &
      The total methane emissions for the year 2030 is 37.74 for Agriculture \\
      Aggregation & Count &  ~ & ~ \\
      \rowcolor{green!20}
      Trends & Comparisons &
      \begin{lstlisting}[language=Fluid]
         trendWord (findWithKey' "model" "BiLSTM" tableData).time\_s (findWithKey' "model" "LSTM" tableData).time\_s "growing from" "shrinking to" "equal to"
      \end{lstlisting}
      & growing from \\
      \rowcolor{green!20}
      Trends & Ranks &
      \begin{lstlisting}[language=Fluid]
         let pos = findIndex "model" "CNN" (insertionSort cmpTime tableData) in rankLabel "lowest" pos
      \end{lstlisting}
      & lowest \\
      Adjectives & Graded adjectives  &  ~ & ~ \\
      References to visual elements and their parts (mereology) & ~ & ~ & ~ \\
      \bottomrule
   \end{tabular}
   \caption{Example expressions generated by the Authoring Assistant, classified by type. In green, the expression is already tested.}
   \label{tab:fluid_examples}
   \renewcommand{\arraystretch}{1.0}
\end{table}
